---
title: "Iris dataset example"
output:
  rmdformats::html_clean:
    fig_width: 6
    fig_height: 6
    highlight: pygments
---


```{r knitr_init, echo=FALSE, results="asis", cache=FALSE}
library(knitr)

## Global options
options(max.print="75")
opts_chunk$set(fig.path="out/",
               echo=FALSE,
	       cache=TRUE,
               cache.path="cache/",
               prompt=FALSE,
               tidy=TRUE,
#               background=".95,.95,.95",
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r init,  echo=FALSE, results="hide"}
library(ggplot2)
library(dplyr)

data(iris)
```

# Output examples

## Syntax highlighting

Here is a sample code chunk, just to show that syntax highlighting works as expected.

```{r sh, echo=TRUE, eval=FALSE}
# create an html dependency for jquery-ui
html_dependency_jquery_ui <- function() {
  htmlDependency(name = "jquery-ui",
                 version = "1.10.4",
                 src = system.file("template/jquery-ui-1.10.4", package="rmdformats"),
                 script = "jquery-ui-1.10.4.custom.min.js")
}
```


## Verbatim

Here is the structure of the `iris` dataset.

```{r iris_str, echo=TRUE}
str(iris)
```

## Table

Here is a sample table output.

```{r iris_table, results='asis'}
tab <- iris %>%
             group_by(Species) %>%
             summarise(Sepal.Length=mean(Sepal.Length),
                       Sepal.Width=mean(Sepal.Width),
                       Petal.Length=mean(Petal.Length),
                       Petal.Width=mean(Petal.Length))
kable(tab)

```

Here we display a crosstab displayed in several different ways with a "pills"
interface. To do this, just pass your `table()` result to the `pilltabs()`
function.

```{r iris_pilltabs, results='asis'}

iris$seplc <- cut(iris$Sepal.Length,3)
tab <- table(iris$Species, iris$seplc)
pilltabs(tab)

```


# Figures

Here is an histogram.

```{r iris_hist}
ggplot(data=iris) +
    geom_histogram(aes(x=Petal.Width)) +
    facet_grid(Species~.)

```

And a wonderful scatterplot, with a caption.

```{r iris_scatter1, fig.cap="This is a caption"}
ggplot(data=iris) + geom_point(aes(x=Petal.Width, y=Petal.Length, color=Species))
```

# Mathjax

And finally, an incredibly complex equation :

$$ y = \sqrt{\frac{1}{x}} $$
