

```{r setup, include=FALSE}
library(knitr)
library(rmdformats)


## Global options
options(max.print = "75")
opts_chunk$set(echo = FALSE,
	             cache = FALSE,
               prompt = FALSE,
               tidy = FALSE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```

# Code and tables

## Syntax highlighting

Here is a sample code chunk, just to show that syntax highlighting works as expected.

```{r sh, echo=TRUE, eval=TRUE}
say_hello <- function (name) {
  paste("Hello,", name, "!")
}

say_hello("world")
```


## Verbatim

Here is the structure of the `penguins` dataset.

```{r penguins_str, echo=TRUE}
library(palmerpenguins)
str(penguins)
```

## Table

Sample table output.

```{r table}
tab <- table(penguins$island, penguins$species)
kable(tab)
```

Sample `DT:datatable` output.

```{r dt}
library(DT)
DT::datatable(penguins)
```

Here is a crosstab displayed in several different ways with a "pills"
interface. To do this, just pass your `table()` result to the `pilltabs()`
function.

```{r pilltabs, results="asis"}
tab <- table(penguins$sex, penguins$species)
pilltabs(tab)

```

# Styling

A simple list : 

- one mississipi
- two mississipi
- three mississipi


A blockquote :

> Oh ! What a nice blockquote you have here. Much more wonderful than a classical Lorem Ipsum, really.

And we could also [include links](https://www.r-project.org/) or simply URLs like this : https://www.r-project.org/

An incredibly complex equation :

$$ y = \sqrt{\frac{1}{x + \beta}} $$


# Figures

Here is an histogram.

```{r hist}
library(ggplot2)
ggplot(data = penguins) +
    geom_histogram(aes(x = body_mass_g)) +
    facet_grid(species~.)

```

And a wonderful scatterplot, with a caption.

```{r scatter, fig.cap="This is a scatterplot"}
ggplot(data = penguins) + 
  geom_point(aes(x = bill_length_mm, y = bill_depth_mm))
```


